
{\bf Peer-Reviewed Conference and Journal Publications}
\begin{bulletlist}

\item Kanit Wongsuphasawat, Zening Qu, Dominik Moritz, Riley Chang, Felix Ouk, Anushka Anand, Jock Mackinlay, Bill Howe, Jeffrey Heer. 2017
\textbf{Voyager 2: Augmenting Visual Analysis with Partial View Specifications}
ACM Human Factors in Computing Systems (CHI) (2017)

\item Dylan Hutchison, Jeremy Kepner, Vjay Gadepally, Bill Howe. 2016.
\textbf{From NoSQL Accumulo to NewSQL Graphulo: Design and utility of graph algorithms inside a BigTable database}
High Performance Extreme Computing Conference (HPEC) (2016)

\item Shrainik Jain, Dominik Moritz, Bill Howe, Ed Lazowska. 2016.
\textbf{SQLShare: Results from a Multi-Year SQL-as-a-Service Experiment}
SIGMOD (2016).

\item Kanit Wongsuphasawat, Dominik Moritz, Anushka Anand, Jock Mackinlay, Bill Howe, Jeffrey Heer. 
\textbf{Voyager: Exploratory analysis via faceted browsing of visualization recommendations}
Visualization and Computer Graphics, IEEE Transactions on 22(1) (2016).

\item  Jeremy Hyrkas, Bill Howe, \textbf{MusicDB: Relational Approach for Numeric Longitudinal Music Analytics}
International Society on Music Information Retrieval (2016).

\item Dominik Moritz,Daniel Halperin,Bill Howe and Jeffrey Heer. 2015.
\textbf{Perfopticon: Visual Query Analysis for Distributed Databases}.
\emph{EuroVis} (2015).

\item Hyrkas, Jeremy, Daniel Halperin, and Bill Howe. 2014. 
\textbf{Time-Varying Clusters in Large-Scale Flow Cytometry}, \emph{Innovative Applications of Artificial Intelligence} (2014)

\item Alawini, Abdussalam, David Maier, Kristin Tufte, and Bill Howe. 2014. 
\textbf{Helping scientists reconnect their datasets}. \emph{Proc. of the 22nd 
Scientific and Statistical Database Management Conference SSDBM} (2014).

\item Upadhyaya, Prasang, Nick R. Anderson, Magdalena Balazinska, Bill
Howe, Raghav Kaushik, Ravishankar Ramamurthy, and Dan Suciu. 2013. \textbf{Stop
that query! The need for managing data use}. \emph{Sixth Biennial Conference 
on Innovative Data Systems Research {CIDR}} (2013).

\item Halperin, Daniel, Konstantin Weitz, Bill Howe, Francois Ribalet, Mark A. Saito,
and E. Virginia Armbrust. 2013. \textbf{Real-time Collaborative Analysis with
(almost) Pure SQL: A Case Study in Biogeochemical Oceanography}.
\emph{Proc. of the 21st Scientific and Statistical
Database Management Conference (SSDBM)} (2013). 

\item Perry, Daniel, Bill Howe, Alicia M. F. Key, Cecilia Aragon. 2013. 
\textbf{VizDeck: Streamlining Exploratory Visual Analytics of Scientific Data}.
\emph{iConference 2013 Proceedings} (2013) pages 338--350. doi:10.9776/13206 

\item Koutris, Paraschos, Prasang Upadhyaya, Magdalena
Balazinska, Bill Howe, and Dan Suciu. 2013. \textbf{Toward Practical Query
Pricing with QueryMarket}. \emph{SIGMOD conference} (2013), 613--624.

\item Koutris, Paraschos, Prasang Upadhyaya, Magdalena Balazinska, Bill
Howe, and Dan Suciu. 2012. \textbf{Query-based data pricing}. \emph{Proceedings of the 31st ACM SIGMOD-SIGACT-SIGART Symposium on Principles of Database Systems {PODS}} (2012),
167--178. 

\item Kwon, YongChul, Magdalena
Balazinska, Bill Howe, and Jerome A. Rolia. 2012. \textbf{SkewTune: Mitigating
Skew in Mapreduce Applications}. \emph{SIGMOD conference} (2012), pages 25--36 (currently the most-cited paper from SIGMOD 2012).

\item Shaw, Marianne, Bill Howe, Paris Koutris, and
Dan Suciu. 2012. \textbf{Optimizing Large-Scale Semi-Naive Datalog Evaluation in
Hadoop}. \emph{Datalog 2.0} (2012). 

\item Howe, Bill, Alicia Key, Daniel Perry, and Cecilia R. Aragon. 2012. 
\textbf{VizDeck: A card game metaphor for fast visual data exploration}. \emph{Proceedings of the 30th International Conference on Human Factors in Computing Systems} (2012), pages 1667--1672. 

\item AlSayyad, Yusra, Simon K. Krughoff, Bill Howe, Andrew J Connolly, Magdalena Balazinska,
and Jones, Lynne. 2011. \textbf{Towards efficient and precise queries over ten million asteroid trajectory models}, \emph{Proc. of the 23rd Scientific and Statistical
Database Management Conference (SSDBM)} (2011), pages 568--570.

\item Balazinska, Magdalena, Bill Howe, and Dan Suciu,
\textbf{Data Markets in the Cloud: An Opportunity for the Database Community},
\emph{Proceedings of the VLDB Endowment} PVLDB, 4, 12, 2011. 

\item Vo, Huy, Brian Summa, Joao Comba, Juliana Freire, Bill Howe, Claudio Silva, and Valerio
Pascucci. 2011. \textbf{Parallel visualization on large clusters using
mapReduce}. \emph{{IEEE} Symposium on Large-Scale Data Analysis and Visualization, {LDAV}}
(2011)

\item Howe, Bill, Garret Cole, Emad Souroush, Paraschos Koutris, Alicia Key, Nodira
Khoussainova, and Leilani Battle. 2011. \textbf{Database-as-a-service for Long
Tail Science}. \emph{Proc. of the 23rd Scientific and Statistical
Database Management Conference (SSDBM)} (2011). 

\item Grochow, Keith, Mark Stoermer, James Fogarty, Charlotte Lee, Bill Howe, and Ed Lazowska. 2010. \textbf{COVE: A Visual Environment for Multidisciplinary Ocean Science Collaboration},
\emph{IEEE Sixth International Conference on eScience (eScience)}, pages 269--276.

\item Kwon, YongChul, Dylan Nunley, Jeffrey P Gardner, Magdalena Balazinska, Bill Howe, and Sarah Loebman. 2010. \textbf{Scalable clustering algorithm for N-body simulations in a shared-nothing cluster}, \emph{Proc. of the 22nd Scientific and Statistical
Database Management Conference (SSDBM)}, (2010), pages 132--150.

\item Kwon, YongChul, Magdalena Balazinska, Bill Howe, and Jerome Rolia.
2010. \textbf{Skew-resistant parallel processing of feature-extracting
scientific user-defined functions}. \emph{Proc. of the ACM Symposium on
Cloud Computing (SOCC)} (2010). 

\item Bu, YingYi, Bill Howe, Magdalena Balazinska, and Michael Ernst. 2010.
\textbf{HaLoop: Efficient iterative data processing on~large~clusters}.
\emph{Proc. of International Conf. on Very Large Databases (VLDB)} (Selected for Best of VLDB Issue of VLDB Journal; currently most-cited paper from VLDB 2010, a premier database conference)

\item Grochow, Keith, Bill Howe, Mark Stoermer, and Ed Lazowska. 2010. 
\textbf{Client + cloud: Seamless
architectures for visual data analytics in the ocean sciences}.
\emph{Proceedings of the 22nd international conference on scientific and
statistical database management (SSDBM)} (2010). 

\item Howe, Bill, Harrison Green-Fishback, and David Maier. 2009. \textbf{Scientific Mashups:
Runtie-Configurable Data Product Ensembles}. \emph{Proceedings of the
21st international Conference on Scientific and Statistical Database
Management (SSDBM)} (2009). 

\item Howe, Bill, Peter Lawson, Renee
Bellinger, Erik Anderson, Emanuele Santos, Juliana Freire, Carlos
Scheidegger, Antonio Baptista, and and Claudio T. Silva. 2008.
\textbf{End-to-End eScience: Integrating Workflow, Query, Visualization, and
Provenance at an Ocean Observatory}. \emph{4th iEEE international
Conference on eScience (eScience)} (2008).

\item Howe, Bill, David Maier, and Laura Bright. 2007. \textbf{Smoothing the ROI
curve for scientific data management applications}. \emph{Proceedings of
the Third Biennial Conference on Innovative Data Systems Research (CIDR)} 
(2007). 

\item Howe, Bill and David Maier. 2005. \textbf{Retrofitting a Data Model to Existing
Environmental Data}. \emph{Proceedings of the 17th international
conference on Scientific and Statistical Database Management (SSDBM)} 
(Santa Barbara, CA, June 2005). 

\item Howe, Bill, and David Maier. 2004.
\textbf{Algebraic Manipulation of Scientific Datasets}. 
\emph{Proceedings of the 30th International Conference on Very Large Data
bases} (2004) (Selected for Best of VLDB Issue of VLDB Journal). 

\item Marianne Koch, Lois Delcambre,
Patricia Toccalino, Eric Landis, Fred Phillips, Tim Tolle,
Len Shapiro, Nicole Steckler, David Maier, Mathew Weaver,
Shawn Bowers, Balbinder Banga,
Jason Brewster, Afrem Gutema, Sudarshan Murthy, Bill Howe, Rupa Tummala,
Julia Norman, Kirsten Zillman,
David Drake, Craig Palmer,
Ashley Burt. 2003. \textbf{The Forest Portal: a Multidisciplinary Project}, 
  \emph{Proceedings of the 2003 annual national conference on Digital government research},
(2003), pages 1--4.

\item Weaver, Mathew, Bill Howe, Lois Delcambre, Tim Tolle, and David Maier. 2002. 
\textbf{Representing, exploiting, and extracting metadata using metadata++},
\emph{Proceedings of the 2002 annual national conference on Digital government research},
(2002), pages 1--7.

\end{bulletlist}


{\bf Journal Articles}
\begin{bulletlist}

\item \textbf{Deep Curation: Distant Zero-shot Learning for Expression Dataset Labeling}. 2017.
Maxim Grechkin, Hoifung Poon, Bill Howe.
Nature Methods (in prep)

\item \textbf{Viziometrics: Analyzing visual information in the scientific literature}. 2017.
Poshen Lee, Jevin West, Bill Howe.
IEEE Big Data Journal (to appear) (arXiv:1605.04951)

\item \textbf{Scalable and Efficient Flow-Based Community Detection for Large-Scale Graph Analysis}. 2016.
Seung-Hee Bae, Daniel Halperin, Jevin West, Martin Rosvall, Bill Howe. 
Transactions on Knowledge Discovery from Data.

\item \textbf{Scalable clustering algorithms for continuous environmental flow cytometry}. 2016.
Jeremy Hyrkas, Sophie Clayton, Francois Ribalet, Daniel Halperin, E. Virginia Armbrust, Bill Howe. 
Bioinformatics 32(3)

\item \textbf{The Database Group at the University of Washington}. 2014.
Balazinska, Magdalena, Bill Howe, Dan Suciu,
\emph{ACM SIGMOD Record}, 43, 1, pages 39--44

\item \textbf{Hadoop's adolescence: An analysis of hadoop usage in scientific workloads}. 2013.
YongChu Kwon, Kai Ren, Magdalena Balazinska, and Bill Howe.
\emph{PVLDB}

\item \textbf{Collaborative Science Workflows in SQL}. 2013.
Bill Howe, Francois Ribalet, Daniel Halperin, Sagar Chitnis, and E. Virginia Armbrust.
\emph{Computing in Science \& Engineering,
Special Issue on Science Data Management}. 15, 3, pages 22--31, 
doi:10.1109/MCSE.2013.42

%\item Howe, Bill, Francois Ribalet, Daniel Halperin, Sagar Chitnis, E Virgnia Armbrust. 
%2013. SQLShare: Scientific Workflow via Relational View Sharing},
%\emph{Computing in Science \& Engineering}, Special Issue on Science Data Management, 15, 2 (2013)

\item \textbf{Advancing Declarative Query in the Long Tail of Science}. 
Bill Howe and Daniel Halperin. 2012. 
\emph{IEEE Data Engineerin Bulletin},
35, 3. pages 16--26.

\item \textbf{The HaLoop approach to large-scale iterative data analysis}. 2012.
Yingyi Bu, Bill Howe, Magdalena Balazinska, and Michael
Ernst.
\emph{Special Issue: Best of VLDB 2010} VLDB Journal, 21, 2 (2012).

\item \textbf{Bioinformatics and data-intensive scientific discovery in the beginning of the 21st century}. 2011.
Barga, Roger, Bill Howe, David Beck, Stuart Bowers, William Dobyns, Winston Haynes, 
Roger Higdon, Chris Howard, Christian Roth, Elizabeth Stewart and others.
\emph{Omics: A Journal of Integrative Biology}, 15, 4 (2011), pages 199--201

\item \textbf{Data Markets in the Cloud: An Opportunity for the Database Community}. 2011.
Magdalena Balazinska, Bill Howe, and Dan Suciu,
\emph{Proceedings of the VLDB Endowment} PVLDB, 4, 12. 

\item \textbf{Astronomy in the Cloud: Using MapReduce for Image Coaddition}. 2010.
Keith Wiley, Andrew J. Connolly, Jeffrey P. Gardner,
               K. Simon Krughoff, Magdalena Balazinska,
               Bill Howe, YongChul Kwon, Yingyi Bu. 2010.
\emph{CoRR}, abs/1010.1015.

\item \textbf{Scientific exploration in the era of ocean observatories}.
Antonio Baptista, Bill Howe, Juliana Freire, David Maier, 
and Claudio T. Silva. 2008.
\emph{Computing in Science and Engineering}. 10, 3 (2008), 53--58.

\item \textbf{Logical and Physical Data Independence for File-based Scientific Applications}. 
Bill Howe and David Maier. 2004. 
\emph{IEEE Data Eng. Bull.} 27, 4, 30--37. 

\item \textbf{A language for spatial data manipulation}. 2003.
Bill Howe, David Maier, and Antonio Baptista. 
\emph{Journal of Environmental Informatics}. 2, 2 

\item \textbf{Algebraic manipulation of scientific datasets}. 
Bill Howe and David Maier. 2004. 
\emph{VLDB Journal:
The International Journal On Very Large Data Bases (Special Issue: Best of VLDB 2004)}. 14, 4.

\end{bulletlist}

{\bf Tech Reports}

\begin{bulletlist}
\item Myers, Brandon, Daniel Halperin, Jacob Nelson, Mark Oskin, Luis Ceze, and Bill Howe.
\textbf{Radish: Compiling efficient query plans for distributed shared memory}.
\end{bulletlist}

{\bf Book Chapters}

\begin{bulletlist}

\item Howe, Bill, 2014. \textbf{Reproducibility, Virtual Appliances, and Cloud Computing}, 
Chapter 10 in Victoria Stodden, Friedrich Leisch, Roger D. Peng (Ed.) 
\emph{Implementing Reproducible Research}, Chapman and Hall/CRC.

\item Balazinska, Magdalena, Bill Howe, Parachos Koutris, Dan Suciu and Prasang Upadhyaya. 2013. 
\textbf{A Discussion on Pricing Relational Data}, In Search of Elegance in the Theory and Practice of Computation, pages 167--173, Springer Berlin Heidelberg.

\item Howe, Bill, 2013. 
\textbf{Transforming Data into the Appropriate Science Context}, Chapter 11 in Terence Critchlow, Kerstin Kleese van Dam (Ed.) \emph{Data-Intensive Science}, 
Chapman and Hall/CRC.

\item Howe, Bill and Magda Balazinska, 2012. 
\textbf{Beyond MapReduce: New Requirements for Scalable Data Processing}, Chapter 8 in Ian Gorton and Deborah K. Gracio (Ed.), \emph{Data-Intensive Computing}, Cambridge University Press.

\end{bulletlist}

{\bf Peer-Reviewed Demonstration Papers}
\begin{bulletlist}

\item Halperin, Daniel, Victor Teixeira de Almeida, Lee Lee Choo, Shumo Chu, 
Parachos Koutris, Dominik Moritz, Jennifer Ortiz, Vaspol Ruamviboonsuk, Jingjing Wang, 
Jingjing and Andrew Whitaker, Shengliang Xu, Magdalena Balazinska, Bill Howe, Dan Suciu, 
\textbf{Demonstration of the Myria big data management service},
\emph{Proceedings of the 2014 ACM SIGMOD International Conference on Management of Data},
(2014), pages 881--884.

\item Upadhyaya, Prasang, Nick R. Anderson, Magdalena Balazinska, Bill
Howe, Raghav Kaushik, Ravishankar Ramamurthy, and Dan Suciu. 2013. 
\textbf{The power of data use management in action}. \emph{SIGMOD} (2013),
pages 1117--1120. 

\item Key, Alicia, Bill Howe, Daniel
Perry, and Cecilia R. Aragon. 2012. 
\textbf{VizDeck: Self-organizing dashboards for visual analytics}. 
\emph{SIGMOD conference} (2012), 681--684.

\item Howe, Bill, Garret Cole, Nodira Khoussainova, Leilani Battle. 2011.
\textbf{Automatic Example Queries for Ad Hoc Databases},
\emph{Proceedings of the 2011 ACM SIGMOD International Conference on Management of data}. (2011), pages 1319--1322

\item Howe, Bill, and David Maier. 2005. 
\textbf{Querying and Visualizing Gridded Datasets for eScience}. \emph{21st international conference on
data engineering (ICDE '05) (demo)} (Tokyo, Japan, 2005). 

\end{bulletlist}

{\bf Peer-Reviewed Workshop Papers}
\begin{bulletlist}

\item Shrainik Jain, Dominik Moritz, Bill Howe. 2016.
\textbf{High variety cloud databases}
Data Engineering Workshops (ICDEW), co-located with VLDB (2016)

\item Kanit Wongsuphasawat, Dominik Moritz, Anushka Anand, Jock Mackinlay, Bill Howe, Jeff Heer. 2016.
\textbf{Towards a general-purpose query language for visualization recommendation}
Proceedings of the Workshop on Human-In-the-Loop Data Analytics (HILDA), co-located with SIGMOD (2016)

\item  Shrainik Jain, Dominik Moritz, Bill Howe. \textbf{High Variety Cloud Databases},  
Workshop on Cloud Data Management (CloudDM) (co-located with ICDE) [invited keynote] (2016)

\item Poshen Lee, Jevin West, Bill Howe. 
\textbf{VizioMetrix: A Platform for Analyzing the Visual Information in Big Scholarly Data}
BigScholar Workshop (co-located at WWW) 2016

\item Joslyn, Cliff, Sutanay Choudhury, David Haglin, Bill Howe, Bill Nickless, Bryan Olsen. 2013. Massive-Scale Cyber Traffic Analysis: A Driver for Graph Database Research,
\emph{First International Workshop on Graph Data Management Experiences and Systems} GRADES (2013).

\item Myers, Brandon, Jeremy Hyrkas, Daniel Halperin, and Bill
Howe. 2013. \textbf{Compiled plans for in-memory path-counting queries}.
\emph{Proceedings of the 1st international workshop on In Memory Data
Management and Analytics, IMDM} (2013), 25--37. 

\item Howe, Bill and Garret Cole. 2010. 
\textbf{SQL is dead; long live SQL: Lightweight query services for ad hoc research data}.
\emph{4th Microsoft eScience Workshop} (2010)

\item Loebman, Sarah, Dylan Nunley, YongChul Kwon, Bill Howe, Magdalena Balazinska, Jeffrey P Gardner, \textbf{Analyzing massive astrophysical datasets: Can Pig/Hadoop or a relational DBMS help?}, 
\emph{IEEE International Conference on Cluster Computing} CLUSTER (2009), pages 1--10.

\item Suciu, Dan, Andrew J Connolly, and Bill Howe. 2009. 
\textbf{Embracing Uncertainty in Large-Scale Computational Astrophysics}.
\emph{Proceedings of the Workshop on Management of Uncertain Data}, (2009),
  pages 63--77.

\item Howe, Bill, Huy Vo, Claudio Silva, and Juliana
Freire. 2009. \textbf{Query-driven visualization in the cloud with mapReduce}.
\emph{Fourth workshop on Ultrascale Visualization} (2009). 

\item Howe, Bill, David Maier, Nicolas Rayner, and James
Rucker. 2008. \textbf{Quarrying dataspaces: Schemaless profiling of unfamiliar
information sources}. \emph{Data engineering workshop, 2008. iCDEW 2008.
iEEE 24th international conference on} (2008), 270--277. 

\item Howe, Bill, and Roger Barga.
2008. \textbf{The eScience Appliance: Provisioning an Inexpensive Bottom-Up
Cyberinfrastructure}. \emph{2nd microsoft eScience workshop, in
conjunction with eScience 2008} (2008). 

\item Bright, Laura, David Maier, and Bill Howe. 2006. \textbf{Managing the
forecast factory}. \emph{Proceedings of the ICDE Workshop on Workflow and
Data Flow for Scientific Applications (SciFlow)} (2006). 

\item Howe, Bill, Kuldeep Tanna, Paul Turner, and David Maier. 2004.
\textbf{Emergent semantics: Towards self-organizing scienitifc metadata}.
\emph{Proceedings of Semantics for a Networked World: Semantics for Grid
Databases} (Paris, France, June 2004). 

\item Howe, Bill and David Maier. 2002. \textbf{Modeling data product generation},
Workshop on Data Derivation and Provenance (Chicago, IL, 2002).
\end{bulletlist}

{\bf Peer-Reviewed Abstracts, Talks, Posters}
\begin{bulletlist}

\item Ren, Kai, Garth Gibson, YongChul Kwon, Magda Balazinska and Bill Howe. 2012.
Hadoop's Adolescence; A Comparative Workloads Analysis from Three Research Clusters,,
\emph{High Performance Computing, Networking, Storage and Analysis (SCC)}, 
pages 1453--1453, 2012

\item AlSayyad, Yusra, Simon Krughoff, Andrew J. Connolly,  L. Jones, Tomas Budavari, and Bill Howe. 2011. Efficient Prediction of Asteroid Positions from Solar System Models, 
\emph{Bulletin of the American Astronomical Society}, 43 (2011).

\item Fishback, Harrison-Green, and Bill Howe. 2008. Scientific mashups:
Runtime-configurable data product ensembles. \emph{4th iEEE
international conference on e-science (eScience) (poster)} (2008).

\item Bill Howe and Nicholas
Hagerty and Ethan Van Matre and David Maier and Antonio Baptista and
Charles Seaton, Paul Turner. 2007. The Ocean Appliance: Complete
Platform Provisioning for Low-Cost Data Sharing. \emph{Proceedings of
the OCEANS 2007 mTS/IEEE conference} OCEANS (2007). 

\end{bulletlist}

